---
title: "Friedman Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Friedman Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
library(Friedman)
library(dplyr)
library(ggplot2)
```

## Introduction

The **Friedman** package provides simple, beginner-friendly tools for exploring the
cleaned version of the **birthwt** dataset from the MASS library. This vignette walks
through how to load the data, summarize birth weight trends, and create quick
visualizations using the package functions.

## Loading the Data


```{r}
data <- bw_data()
head(data)
```

## Summarizing Birth Weight

We can summarize the average birth weight by any grouping variable.
For example, here is the summary by *smoking status*:


```{r}
bw_summary(data, "smoke")
```

## Creating Plots

A scatterplot can be made to compare categories like *age* and *birth weight*. 
Color and trendline are optional, and trendline is TRUE by default.


```{r}
bw_plot(data, "age", "bwt", color = "smoke", trend = TRUE)
```

## Conclusion

The Friedman package provides simple but useful tools for students and beginners
who want to explore patterns in the birth weight dataset without writing complex
code. This vignette demonstrates the core workflow: load the data, summarize
important variables, and visualize relationships quickly and clearly.
